Creating a bushfire dataset \\ An adventure in wrangling spatial data

### 2016-01-27 data_processing.tex
add make_figures NB NOT FINAL VERSION

 \sec

	From the fire occurrence dataset this study used the date and coordinates of the fire. The coordinates were given in the Australian Map Grid (AMG66), a coordinate reference system derived from a Universal Transverse Mercator(UMT) projection of latitudes and longitudes on the Australian Geodetic Datum (AGD) \citep{featherstone96}. To merge the meteorological data set and the fire occurrence dataset I needed to convert from this UMT projection to longitude and latitude using the sp package in R \citep{sp08}.

>>>>

	\section{Fire Ignition}

	The fire ignitions data came in CSV format with a date and time, brigade and coordinates. The coordinates were given in the Australian Map Grid (AMG66), a coordinate reference system derived from a Universal Transverse Mercator(UMT) projection of latitudes and longitudes on the Australian Geodetic Datum (AGD) \citep{featherstone96} in UMT projection each coordinate has a zone, an easting and northing. To merge the meteorological data set and the fire occurrence dataset we convert from this UMT projection to longitude and latitude using the sp package in R \citep{sp08}.
